\section{Introduction}

%This paper is organized in the following way: first there will be a brief introduction whose purpose is to
%frame the majority of our arguments in a manner that will provide meaningful context throughout the duration
%of the paper. Second we introduce some of the primary topics that will be covered in the heart of this paper. 
%The next portion of the paper deals with specific examples of our broad claims in the introduction, as well as 
%a case study to support each argument. Finally we will conclude our paper with an examination of the evidence we
%presented and a discussion of how our claims were supported. 
%
%
%We will begin by examining protocol's and their diverse roll in the common marketplace. The purpose of any 
%protocol is two fold: first it is supposed to help new business enter the market since there has already been an
%established precedent to follow, secondly it is to allow the work of multiple businesses to flow together 
%seamlessly. 


The organization of this paper is as follows. First there will be a brief 
introduction section where the paper's format, framing, topics, and relevant previous work will
be introduced.After the introduction there will be a general discussion of several different
types of networking protocols and standards, along with corresponding case 
studies. The order that these protocols will be discussed is: network size
increase and the IP address problem, global networking and countries who don't
conform, and \textbf{BLAH}. Finally we will conclude by examining the 
principal characteristics that each of these protocols have in common in 
relation to new businesses entering a market.


The focus of our research is in regards to the relative ease or difficulty 
that an entrepreneur faces when deciding to enter a market place that is 
saturated with technological protocols. Because of the rapid advancement in 
networking and computing technologies that mankind has experienced in the past
century, these protocols have become more and more complex. Modern computer 
networking touches almost every aspect of any successful business; from 
marketing and advertisement to accepting payment and collecting customer data.
Hence it becomes necessary to inspect the costs and benefits of each of the 
protocols that must be adapted before considering entrance into a market place. 


There has been much interest and research in the over all sustainability of 
certain networking protocols\cite{4124025}. In our paper we will examine the impact of
exponential network growth and the problems that are posed with IP addressing on an expanding
market. There has also been work done on analyzing the development of protocols
\cite{4375858}. There has also been research into relaying older protocols to new uses
\cite{6296937}. And there is much current work being done on coming up with new
protocols\cite{5977081}. 


